---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tst - Timestamped Suffix Trees

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/pmcharrison/tst?branch=master&svg=true)](https://ci.appveyor.com/project/pmcharrison/tst)
[![Travis build status](https://travis-ci.org/pmcharrison/tst.svg?branch=master)](https://travis-ci.org/pmcharrison/tst)
[![Coverage status](https://coveralls.io/repos/github/pmcharrison/tst/badge.svg)](https://coveralls.io/r/pmcharrison/tst?branch=master)

`tst` is an R package for building timestamped suffix trees (TSTs). 
TSTs are [suffix trees](https://en.wikipedia.org/wiki/Suffix_tree)
that store timestamps for each state transition in the training sequence(s).
Given a sequence of consecutive symbols, the TST can efficiently return 
the timepoints when this sequence occurred in the training data, 
the symbols that followed this sequence in the training data,
and the timepoints when these continuation symbols were observed.

For an interactive demo, visit http://shiny.pmcharrison.com/suffix-tree-demo.

## Installation

```
install.packages("devtools") # if you don't have devtools already installed
devtools::install_github("pmcharrison/tst")
```

## Example use

```{r, include = TRUE, echo = TRUE}
library(tst)

# Build and visualize a simple suffix tree
t <- new_tree()
add_seq(t, c("a", "b", "c", "a", "b"))
plot(t)

# Incrementally visualize the building of a suffix tree
t <- new_tree()
add_seq(t, c("a", "b", "c", "a", "b"), visual = TRUE)

# Search for n-grams
when_ngram(t, c("a", "b"))
count_ngram(t, c("a", "b"))
```
